Operator evolution from the similarity renormalization group and the Magnus expansion

### 2019-09-27 Notes/Operator_evolution/operator_evolution.tex
Added a couple momentum projection operator figures to the notes

\noindent{%
-- SRG operator evolution for different potentials and generators.
}
\\
-- General questions to address: universality for operators, different generators.
\\
-- Momentum projection operator.
%
\begin{itemize}
	\item Contours and general behavior: SRG transformation shifts strength of operator to low-momentum.
	\item Deuteron momentum distributions. Why does this make sense with the transformed operators?
	\item Diagonals and far off-diagonals. Universality.
	\item Same questions but with figures of the integrand.
\end{itemize}
%
-- Note, the unitary transformations and evolved wave functions for different potentials are not the same (at low momentum too) swhich implies that evolved operators cannot have the same universality property as the evolved potentials since they are dependent on the evolved wave functions.
\\
-- $\hat{r}^2$ operator.

>>>>

\noindent{%
-- SRG operator evolution for different potentials and generators.
}
\\
-- General questions to address: universality for operators, different generators.
\\
-- Give relevant equations. Unitary transformation equation.
\\
-- Momentum projection operator.
\\
-- Relevant equations: just the momentum projection operator in momentum-space.
%
\begin{itemize}
	\item Contours and general behavior: SRG transformation shifts strength of operator to low-momentum.
	\item Deuteron momentum distributions. Why does this make sense with the transformed operators?
	\item Diagonals and far off-diagonals. Universality.
	\item Same questions but with figures of the integrand.
\end{itemize}
%
\begin{figure}[H]
	\centering
	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_diag_q3,00_3S1_kvnns_10_106_222_lamb1,5}%
	}

	\subfloat[]{%
	\includegraphics[clip,width=0.9\columnwidth]{SRG_operators/momentum_projection_off-diag_q3,00_3S1_kvnns_10_106_222_lamb1,5}%
	}
	\caption{Diagonal (a) and far off-diagonal (b) matrix elements of the momentum projection operator under SRG transformations with EM N$^3$LO (black), RKE N$^3$LO (red) and Gezerlis et al. N$^2$LO (blue) potentials evolving right to left with Wegner (solid) and block-diagonal (dash-dotted) generators in the $^3$S$_1$ channel. Here, we use $\lambda$ for Wegner evolution and $\Lambda$ for block-diagonal evolution. For block-diagonal evolution, we fix $\lambda=1.5$ fm$^{-1}$.}
	\label{fig:momentum_proj_3S1}
\end{figure}
%
-- Note, the unitary transformations and evolved wave functions for different potentials are not the same (at low momentum too) which implies that evolved operators cannot have the same universality property as the evolved potentials since they are dependent on the evolved wave functions.
\\
-- $\hat{r}^2$ operator.
\\
-- Relevant equations: operator in coordinate-space and Hankel transformation.
